### 2017-04-10 sections/implementation.tex
Update on Overleaf.

But how can be the rank of approximation matrix effectively calculated from the desired approximation error? Here comes useful the interesting property of the singular values:

@@

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (\mtrx{A_{ij}})^{2} = \sum_{i=1}^{k}{\sigma_{i}^{2}},
\label{eq:elem-sqr-sigma-sqr}
\end{equation}

\noindent
where $k=min(m, n)$, i.e. the smallest of two dimensions of the matrix $\mtrx{M}$. The above formula states that the sum of squared elements of matrix $\mtrx{A}$ equals to the sum of squared singular values $\sigma_{i}$ of the same matrix $\mtrx{A}$.

@@

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (\mtrx{A_{ij}} - \mtrx{A'_{ij}})^{2} = \sum_{i=r+1}^{k}{\sigma_{i}^{2}},
\end{equation}

\noindent
where the term on the right-hand side is the sum of squares of those singular values of the matrix $A$ that are going to be cut away by the compression algorithm. The equation can be rewritten using the definition of $MSE$ in \eqref{eq:mse-def} to

\begin{equation}
MSE \times m n = \sigma_{r+1}^{2} + \sigma_{r+2}^{2} + ... + \sigma_{k-1}^{2} + \sigma_{k}^2
\end{equation}

@@

\begin{equation}
(NRMSD \times (X_{max}-X_{min}))^{2} \times m n = \sigma_{r+1}^{2} + \sigma_{r+2}^{2} + ... + \sigma_{k-1}^{2} + \sigma_{k}^2.
\end{equation}

@@

\begin{equation}
e > \frac{\sqrt[]{\frac{\sigma_{r+1}^{2} + \sigma_{r+2}^{2} + ... + \sigma_{k-1}^{2} + \sigma_{k}^2}{m n}}}{X_{max}-X_{min}},
\end{equation}

>>>>

To effectively calculate the final rank of the approximation matrix from the desired approximation error the interesting property of the singular values is used:

@@

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (\mtrx{A}_{ij})^{2} = \sum_{i=1}^{k}{s_{i}^{2}},
\label{eq:elem-sqr-sigma-sqr}
\end{equation}

\noindent
where $k=min(m, n)$, i.e. the smallest of two dimensions of the matrix $\mtrx{M}$. The above formula states that the sum of squared elements of matrix $\mtrx{A}$ equals to the sum of squared singular values $s_{i}$ of the same matrix $\mtrx{A}$.

@@

\begin{equation}
\sum_{i=1}^{m} \sum_{j=1}^{n} (\mtrx{A}_{ij} - \mtrx{A'}_{ij})^{2} = \sum_{i=r+1}^{k}{s_{i}^{2}},
\end{equation}

\noindent
where the term on the right-hand side is the sum of squares of those singular values of the matrix $\mtrx{A}$ that are going to be cut away by the compression algorithm. The equation can be rewritten using the definition of $MSE$ in \eqref{eq:mse-def} to

\begin{equation}
%MSE \times m n = s_{r+1}^{2} + s_{r+2}^{2} + ... + s_{k-1}^{2} + s_{k}^2
MSE \times m n = \sum_{i=r+1}^{k} s_{i}^{2}
\end{equation}

@@

\begin{equation}
%(NRMSD \times (X_{max}-X_{min}))^{2} \times m n = s_{r+1}^{2} + s_{r+2}^{2} + ... + s_{k-1}^{2} + s_{k}^2.
(NRMSD \times (X_{max}-X_{min}))^{2} \times m n = \sum_{i=r+1}^{k} s_{i}^{2}.
\end{equation}

@@

\begin{equation}
e > \frac{\sqrt[]{\frac{\sum_{i=r+1}^{k} s_{i}^{2}}{m n}}}{X_{max}-X_{min}},
\end{equation}
